{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-11-23 thesis/thesis.tex
configure revision changebars
David A. Eckhardt

%\usepackage{fontspec}
\usepackage{mathspec}
\usepackage{xeCJK}

@@

@@

Professor David Eckhardt
provided unending guidance on education, writing, career, life, you name it,
helped revise each semester's iteration of the recruiting lecture with a keen eye for the student mind,
contributed substantially to the design of the survey,
and supplied constant enthusiasm and encouragement that Landslide was a boon to 15-410.
I can't express my gratitude to Dave strongly enough,
even if it took until just this week for half of the Landslide-friendly tests to be included in the official P2 test suite.
%even though three of the Landslide-friendly tests never made it upstream into the official P2 test suite.

@@

\newcommand\revision[1]{#1\xspace}

>>>>

%\usepackage{fontspec}
\usepackage{mathspec}
\usepackage{xeCJK}
\usepackage[xetex]{xechangebar}

@@

%\newcommand\revision[1]{#1\xspace}
\newcommand\revision[1]{\cbstart{}#1\cbend\xspace}
%\newcommand\revisionminor[1]{#1\xspace}
\newcommand\revisionminor[1]{\cbstart{}#1\cbend\xspace}

@@

Professor David A. Eckhardt
provided unending guidance on education, writing, career, life, you name it,
helped revise each semester's iteration of the recruiting lecture with a keen eye for the student mind,
contributed substantially to the design of the survey,
and supplied constant enthusiasm and encouragement that Landslide was a boon to 15-410.
I can't express my gratitude to Dave strongly enough,
even if it took until just this week for half of the Landslide-friendly tests to be included in the official P2 test suite.
%even though three of the Landslide-friendly tests never made it upstream into the official P2 test suite.

@@
